Titeltext

### 2018-07-26 thesis/paper/paper.tex
Added single best value

>>>>

\subsection{Single best value (Q52060874)}
The single best value constraint requires that only one constrained statement per item has the rank preferred.

\begin{table}[H]
\caption{Single best value constraint (Q52060874)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & item statement rank \\
\hline
Violation & \makecell{items with two constrained statements with rank preferred} \\
\hline
Dependency & all item statements and their rank \\
\hline
Rule features & count \\
\hline
\end{tabularx}
\end{table}

Modelling the constraint means a count of all constrained statements with rank preferred is necessary, with a violation constituted if an item has a count of two or higher. Since it is only needed to differentiate between one and many, the rules could be written explicitly.
